Dark matter halo concentrations with a bayesian approach

### 2014-09-13 paper/article.tex
added new plot

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig} 
\usepackage{hyperref}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

@@

We also used these three methods to obtain the concentration for each halo in miniMDR1 and compared the results. As can be seen in the Figures \ref{fig:density-mass}, \ref{fig:density-velocity} and \ref{fig:velocity-mass} the three methods show mutually consistent results. However it can be inferred that the concentration values ​​obtained by the method of circular velocity are higher than those obtained by our method, and also the values ​​obtained by the density method are generally below the results of our method.

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{mass-density.pdf}
\end{center}
\caption{Concentration obtained from the density method against the one obtained in the mass method
    \label{fig:density-mass}}
\end{figure}
\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
\end{center}
\caption{Concentration obtained from the velocity method against the one obtained in the density method
    \label{fig:density-velocity}}
\end{figure}
\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{velocity-mass.pdf}
\end{center}
\caption{Concentration obtained from the mass method against the one obtained in the velocity method
    \label{fig:velocity-mass}}
\end{figure}

\subsection{Concentration as a function of halo mass}
Aditionally we compared those three methods plotting the concentration as a function of the number of particles of each halo

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{concentration.pdf}
\end{center}
\caption{Concentration against number of particles
    \label{fig:concentrations}}
\end{figure}

The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles. Showing that our method has values ​​ranging from those obtained from the other two methods.
\subsection{Implication for comparisons against observations}
FIXME: Ask to Jaime

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig} 
\usepackage{hyperref}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.99\textwidth]{mass-density-velocity.pdf}
\end{center}
\caption{Comparison between the obtained concentrations by the three methods
    \label{fig:mdv}}
\end{figure*}

We also used these three methods to obtain the concentration for each halo in miniMDR1 and compared the results. As can be seen in Figure \ref{fig:mdv} the three methods show mutually consistent results. However it can be inferred that the concentration values ​​obtained by the method of circular velocity are higher than those obtained by our method, and also the values ​​obtained by the density method are generally below the results of our method.

\subsection{Concentration as a function of halo mass}
Aditionally we compared those three methods plotting the concentration as a function of the number of particles of each halo 
%
%\begin{figure}[h!]
%\begin{center}
%  \includegraphics[width=0.48\textwidth]{concentration.pdf}
%\end{center}
%\caption{Concentration against number of particles
%    \label{fig:concentrations}}
%\end{figure}
%
The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles. Showing that our method has values ​​ranging from those obtained from the other two methods.
\subsection{Implication for comparisons against observations}
FIXME: Ask to Jaime
